### 2017-10-11 README.Rmd
add initial pkgdown materials
WIP => Active; misc other changes

[![Travis-CI Build Status](https://travis-ci.org/nhejazi/methyvim.svg?branch=master)](https://travis-ci.org/nhejazi/methyvim)
[![AppVeyor Build  Status](https://ci.appveyor.com/api/projects/status/github/nhejazi/methyvim?branch=master&svg=true)](https://ci.appveyor.com/project/nhejazi/methyvim)
[![Coverage Status](https://img.shields.io/codecov/c/github/nhejazi/methyvim/master.svg)](https://codecov.io/github/nhejazi/methyvim?branch=master)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![MIT license](http://img.shields.io/badge/license-MIT-brightgreen.svg)](http://opensource.org/licenses/MIT)

@@

<!--
Note about shrinkage of influence curves, adapting @smyth2004linear.
Specifically, this is meant to reference my working paper with Alan.

More exposition here....
-->

@@

>>>>

[![Travis-CI Build Status](https://travis-ci.org/nhejazi/methyvim.svg?branch=master)](https://travis-ci.org/nhejazi/methyvim)
[![AppVeyor Build  Status](https://ci.appveyor.com/api/projects/status/github/nhejazi/methyvim?branch=master&svg=true)](https://ci.appveyor.com/project/nhejazi/methyvim)
[![Coverage Status](https://img.shields.io/codecov/c/github/nhejazi/methyvim/master.svg)](https://codecov.io/github/nhejazi/methyvim?branch=master)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![MIT license](http://img.shields.io/badge/license-MIT-brightgreen.svg)](http://opensource.org/licenses/MIT)

@@

<!--
Note about shrinkage of influence curves, adapting @smyth2004linear.
More exposition here....
-->

@@

## References
